---
title: "Retail-Australian_Grocery_Store_Analysis"
author: "Hrudhai Umas"
date: "`r Sys.Date()`"
output: html_document
---
## Retail- Australian Grocery Store Analysis by: Ayush Gupta, Roshan Mettupalli, and Hrudhai Umas

### Step 1: Data Manipulation and Cleaning

1. In this first step, we are loading the packages needed to manipulate and 
clean the data. We are also sorting the dataset to include all the similar
receipt_id's, to sort based on ____. 
```{r message=FALSE}
library(tidyverse)

retail_data <- read_delim("sales_data_2017_2018_data.csv")

retail_data %>% 
  arrange(desc(receipt_id))
```

2. Looking at the data, the team has realized multiple areas where the data
could be cleaned and also many fields which were empty, but can be filled. 
In detail, the field of many _total_buying_price_ are N/A when they are 
supposed to be a value. Additionally, many fields in _unit_buying_price_, _unit_selling_price_, 
_unit_price_margin_, _total_buying_price_ _total_selling_price_ and _total profit_,  
have rounding errors in that it has more than 2 decimal places, which contextually preposterous. We als....

## Rounding Data Columns!

```{r}
# Round the specified columns to 2 decimal places
retail_data <- retail_data %>% 
  mutate(
    unit_buying_price = round(unit_buying_price, 2),
    unit_selling_price = round(unit_selling_price, 2),
    unit_price_margin = round(unit_price_margin, 2),
    total_buying_price = round(total_buying_price, 2),
    total_selling_price = round(total_selling_price, 2),
    total_profit = round(total_profit, 2)
  )

retail_data
```

## Adding Values to unit_buying_price!
```{r}
retail_data <- retail_data %>% 
  mutate(
    unit_buying_price = unit_selling_price - unit_price_margin
  )

retail_data
```

## Adding Values to total_buying_price!
```{r}
retail_data <- retail_data %>% 
  mutate(
    total_buying_price = total_selling_price - total_profit
  )

retail_data
```

## Save File: Cleaning and Manipulation is Done!
```{r}
# Write the updated data to a new file
write_csv(retail_data, "sales_data_2017_2018_data_updated.csv")
```

