---
title: "Retail-Australian_Grocery_Store_Analysis"
author: "Hrudhai Umas"
date: "`r Sys.Date()`"
output: html_document
---
## Retail- Australian Grocery Store Analysis by: Ayush Gupta, Roshan Mettupalli, and Hrudhai Umas

### Data Manipulation and Cleaning

1. In this first step, we are loading the packages needed to manipulate and 
clean the data. We are also sorting the dataset to include all the similar
receipt_id's, to sort based on how many items one individual with that id
has bought!
```{r message=FALSE}
library(tidyverse)

retail_data <- read_delim("sales_data_2017_2018_data.csv")

retail_data %>% 
  arrange(desc(receipt_id))
```

2. Looking at the data, the team has realized multiple areas where the data
could be cleaned and also many fields which were empty, but can be filled. 
In detail, the field of many _total_buying_price_ are N/A when they are 
supposed to be a value. Additionally, many fields in _unit_buying_price_, _unit_selling_price_, 
_unit_price_margin_, _total_buying_price_ _total_selling_price_ and _total profit_,  
have rounding errors in that it has more than 2 decimal places, which is contextually preposterous.
Additionally, we saw that columns such as unit_buying_price and total_buying_price 
were empty for many items and we decided to use mathematical formulas to 
calculate and override those empty values with the correct values!

## Rounding Data Columns!

```{r}
# Round the specified columns to 2 decimal places
retail_data <- retail_data %>% 
  mutate(
    unit_buying_price = round(unit_buying_price, 2),
    unit_selling_price = round(unit_selling_price, 2),
    unit_price_margin = round(unit_price_margin, 2),
    total_buying_price = round(total_buying_price, 2),
    total_selling_price = round(total_selling_price, 2),
    total_profit = round(total_profit, 2)
  )

retail_data
```
## Adding Values to unit_buying_price!

Using the formula, we subtracted the unit_selling_price from the unit_price_margin
to get our unit_buying_price. This can help our data visualizations way more 
accurate as it will have actual data in the field except for just NA.
```{r}
retail_data <- retail_data %>% 
  mutate(
    unit_buying_price = unit_selling_price - unit_price_margin
  )

retail_data
```
## Adding Values to total_buying_price!

Using the formula, we subtracted the _total_selling_price_ from the _total_profit_
to get our _total_buying_price_ This can help our data visualizations way more 
accurate as it will have actual data in the field except for just NA.
```{r}
retail_data <- retail_data %>% 
  mutate(
    total_buying_price = total_selling_price - total_profit
  )

retail_data
```

## Save File: Cleaning and Manipulation is Done!

Finally, after all this is done, we saved our new csv file as such and will 
now use this new dataset to do our project and data analysis!
```{r}
# Write the updated data to a new file
write_csv(retail_data, "sales_data_2017_2018_data_updated.csv")
```
